\chapter*{Preface}

This dissertation is the minimal time path for Lasers. The Laser is one of the classes from Olympic Sailing and it uses one of the smallest boats known as a dinghy. Sailboats can't displace against the wind following a straight line, because of this it is the time related to the optimization of the path and not the distance.  \par 

This thesis has been written to fulfill the graduation requirements of the Master's degree in Bio-Mechanical Design at TU Delft. This project was undertaken at the request of \acrlong{sailctr} where I undertook an internship. My research question was formulated together with professor Sukanta Basu and the \acrshort{sailctr}. In the beginning, the research was difficult since the application of wind models on sports and the research about the Laser's dynamics is limited. The investigation I conducted was extensive and took me to unfamiliar topics, fortunately, all these have allowed me to answer the question of this thesis. I would like to thank my supervisor for his guidance and support during this process. I also wish to thank professor Sukanta Basu for his cooperation and my academic counselor Evert Vixseboxse for his support. \par 

When I pursued a Master in Science at TU Delft I remember what my parents used to tell when I was a kid \textit{"Learning is a never-ending process"}. Learning is more than books and science. Learning is also a process about ourselves. I dedicate this thesis to my parents and siblings, my best friends. Thanks for your support and sincerity. You help me learn how to feel comfortable out of my comfort zone, how to feel close to you despite the distance and even in moments where I doubt about myself. Thank you, Dad, because until I haven't heard from you \textit{No} as an answer. During this time at the Netherlands I have learned and growth as person and as a student in such ways I haven't expected. This process sometimes was challenging, hard to endure and despite these I always got your love and support. You always cheer me and question me when I need it the most. \par 
Finally, I would like to thank all the friends I made during this time you make my days, without you, this process wouldn't be as fun as it was. To my friends Blanca Mayo and Kika, thank you for all your time, conversations and comprehension, I know I always can count on you.\par
\begin{flushright}
Gaby Pardo A  \break
Delft, March 2019
\end{flushright}

