\chapter{Conclusions and Recommendations}
In conclusion, the minimal time path is conformed by the leg-times, start points over the race-lines and directions of the paths. Two of these elements were predicted similarly as the winners using the \acrshort{wrf} wind model with an error in the race-time for less than 5\%. However, the direction of the paths were not predicted accurately for the upwind-mode legs. This because the wind's direction predicted by the model is much larger than 10\degree of the direction reported during the race. \par

The minimal time path algorithm shaped by the wind for Olympic Classes, particularly for the Laser Class has shown sensibility to the scenarios delineated by alternative wind models. Despite the race-times and shapes differences derived from them, it shows that the \acrshort{wrf} wind model with a grid resolution of 1 km and a time step of 10 minutes predict the same start point on all the race-lines as the winner of the race. The race-time resulted using this model was 51 minutes and 11.97 seconds while the winner time was 49 minutes and 4 seconds, the difference between these race times is 2 minutes and 49.03 seconds or 4.26\%. Even when this error is below 5\% the direction of the paths for the upwind-mode legs is opposite to all the top ten winners. In the other hand, the direction of the upwind-mode legs was the same as the winners using the constant and uniform wind scenario. \par

The constant and uniform wind scenario predict the same direction for most of the legs as the top ten winners. The resulting race-time was 53 minutes and 10.38 seconds, the time difference respect to the winner was 4 minutes and 50.62 seconds or 7.82 \%. Accordingly, the start points were not the same for the leg 2 and leg 3. Subsequently, the only leg direction that was not the same neither close was leg 2. \par 
Leg 2 is a downwind-mode leg and none of the scenarios predicted similar directions nor shapes as the top then winners. They sail this leg following shapes that looks like a curve instead of a straight-line. The reason for these shapes are not clear but it could influence by the current direction, particularly the height of waves not considered in this research. Another consideration to account is the ability of the sail-man and the traffic of dinghies especially because this leg is the second one. \par  %one of the reason for this could be the influence of the current over the sailing direction. 

The grid resolution of the wind model is important for the minimal time path estimation. More important is that the locations of the racecourse should be within the area limited by them to avoid the extrapolation of the wind speed and angle at any point of the path. The extrapolation of the values rises errors (\%) for leg-times sailed under upwind-mode larger than 25\% from the leg-times of the winner. %In fact, 
Using the wind measurements from the race the leg 3, sailed under upwind-mode, was in the opposite direction compared with the path of the top ten winners.  If a wind field with these characteristics is not available, then is more accurate to use the average values of both parameters and estimate the minimal path as it was under a constant and uniform wind field. \par 

%The last leg, leg 5 sailed under direct-wind mode was predicted by all the scenarios and sailed by the winners in a straight-line. 
All the scenarios predict a straight-line trajectory for leg 5, the last leg, and the winners sailed it as predicted. Nonetheless, the leg-time in all the scenarios rise an error about 17\% for the \acrshort{wrf} wind model or 11.48\% for the constant and uniform wind field %at least 9.1\% 
respect to the average leg-time from the top ten winners. This means that the speed's boat and therefore the wind's speed estimation were incorrectly. The uncertainty about the speed of the Laser and the wind's speed in addition, to other sources of an error account for this time difference. \par   %account in total for these errors and other sources of it. The other sou non-identified.   
%The Laser model was adapted from the yacht sailboat, this adaptations like the estimation and values of the coefficients as the 
The constant and uniform wind field differs from the \acrshort{wrf} wind model in many aspects, however, the shape of the resulted minimal path of each compared with the paths of the winner's race revesls the effect of the wind direction on it. This difference is more significant than the variations on the race-time for each scenario. The wind's speed affects how fast the dinghy arrives from one point to another, but it is the wind's direction the parameter that orients it and defines the shape of the path. For example, the angle's during the race was 108\degree, while the angle from the \acrshort{wrf} wind model was 149.57\degree. The difference between them is sufficiently large to shape path trajectories with different directions. \par %Because of this, the rule related to the wind shifts range is smaller than the range for the wind's speeds. \par 
\section{Recommendations}
Because of the error in the last leg and on the downwind-mode. This research proposes to review the adaptions made to model the laser boat from the yachts. These adaptations are another source of error and it affects how the wind's speed influence the dinghy's speed. For example, the yacht model assume the location of the \acrshort{ce} at 40\% of the sail's height, the same approach on the Laser could have additional consequences since the resulting locations are close to the sea level and the current and height of the waves could generate frictional forces which are insignificant at higher distances. \par 
The downwind leg's time resulting from all the scenarios were also larger than the times from the winners, although it was as a straight-line. Under this condition, the wind' speed pushes the dinghy basically, so tack maneuvers or changes in the direction which add time to the leg are not required. Therefore, this research proposes to examine the constraints and how the additional time as a consequence of the changes in the direction does not affect the leg in the same way as in the upwind mode. \par 
The last recommendations this research refer with the modeling dimensions of the boat, to review the influence of the position of the sail-man on the dinghy's speed particularly in the downwind and direct wind-mode where the optimal path is a straight-line with the presence of waves and current when the modeling considers the three planes of motion. \par  %respect to the center of gravity for the down
 